\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-26 Writeup/paper.tex
Add the plain data to the data section

Next we go through every packet that tcpdump captured and find the IP that sent us the most packets. We consider that to be the IP that the content actually came from, as long as more than one third of the captured packets came from that IP. Now we have an IP for the website, the CDN, and the actual content, and we run ping and traceroute, as well as querying ipinfo.io for all three of these.

@@

\section{Data?}\label{sec:data} % How is this different from results AND method? >.>
\section{Results}\label{sec:results}
\section{Future Work}\label{sec:futurework}

>>>>

Next we go through every packet that tcpdump captured and find the IP that sent us the most packets. We consider that to be the IP that the content actually came from, as long as more than one third of the captured packets came from that IP. In the event that no single IP was the source of more than one third of the captured packets, we retry up to three times. This retry behaviour gives our test greater stability in the face of existing network traffic. Now we have an IP for the website, the CDN, and the actual content, and we run ping and traceroute, as well as querying ipinfo.io for all three of these.

@@

\begin{itemize}
	\item Different ISPs? \\
	\item All the same location - CONSISTENCY
\end{itemize}

\section{Results}\label{sec:results}
\subsection{Home network}
We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
Below are the results of each run, averaged across ISPs:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
  & Popular Youtube   & 60  & 14  & 14  \\ \hline
  & Soundcloud        & 161 & 162 & 184 \\ \hline
  & Twitch.tv         & 198 & 159 & 172 \\ \hline
2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
  & Popular Youtube   & 63  & 14  & 31  \\ \hline
  & Soundcloud        & 161 & 160 & 165 \\ \hline
  & Twitch.tv         & 193 & 159 & 181 \\ \hline
3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
  & Popular Youtube   & 31  & 23  & 18  \\ \hline
  & Soundcloud        & 179 & 171 & 160 \\ \hline
  & Twitch.tv         & 184 & 159 & 161 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 14 & 14 & 15 \\ \hline
2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 12 \\ \hline
3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 13 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput (KB/s): \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 197.8 \\ \hline
  & Popular Youtube   & 202.6 \\ \hline
  & Soundcloud        & 197.9 \\ \hline
  & Twitch.tv         & 201.2 \\ \hline
2 & Unpopular Youtube & 201.9 \\ \hline
  & Popular Youtube   & 197.8 \\ \hline
  & Soundcloud        & 201.3 \\ \hline
  & Twitch.tv         & 203.1 \\ \hline
3 & Unpopular Youtube & 202.8 \\ \hline
  & Popular Youtube   & 200.4 \\ \hline
  & Soundcloud        & 203.6 \\ \hline
  & Twitch.tv         & 204.9 \\ \hline
\end{tabular}

TODO: Table of "offset from median" of the metrics for each ISP

\subsection{UCT Network}
For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet.

Note that some of the throughput data points are missing, this is because we measure throughput as youtube-dl downloads and in those cases the download finished before we could get a good measure.
\subsubsection{Test case 1}
The first test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
The results are tabulated below:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 18  & 49  & 44  \\ \hline
  & Popular Youtube   & 45  & 19  & 18  \\ \hline
  & Soundcloud        & 179 & 148 & 154 \\ \hline
  & Twitch.tv         & 148 & 155 & 148 \\ \hline
2 & Unpopular Youtube & 21  & 19  & 19  \\ \hline
  & Popular Youtube   & 19  & 26  & 19  \\ \hline
  & Soundcloud        & 148 & 149 & 148 \\ \hline
  & Twitch.tv         & 148 & 148 & 148 \\ \hline
3 & Unpopular Youtube & 3   & 19  & 19  \\ \hline
  & Popular Youtube   & 2   & 45  & 68  \\ \hline
  & Soundcloud        & 148 & 148 & 148 \\ \hline
  & Twitch.tv         & 151 & 154 & 148 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 1484.8  \\ \hline
  & Popular Youtube   & 8560.6  \\ \hline
  & Soundcloud        & 1351.7  \\ \hline
  & Twitch.tv         & 11284.5 \\ \hline
2 & Unpopular Youtube & 7690.2  \\ \hline
  & Popular Youtube   & 8161.3  \\ \hline
  & Soundcloud        & -       \\ \hline
  & Twitch.tv         & 11264.0 \\ \hline
3 & Unpopular Youtube & 7598.1  \\ \hline
  & Popular Youtube   & 9543.7  \\ \hline
  & Soundcloud        & -       \\ \hline  
  & Twitch.tv         & 11233.3 \\ \hline
\end{tabular}

\subsubsection{Test case 2}
The second test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
The results are tabulated below:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
  & Popular Youtube   & 4   & 19  & 21  \\ \hline
  & Twitch.tv         & 148 & 154 & 148 \\ \hline
  & Soundcloud        & 148 & 148 & 0   \\ \hline
2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
  & Popular Youtube   & 4   & 20  & 19  \\ \hline
  & Twitch.tv         & 172 & 154 & 0   \\ \hline
  & Soundcloud        & 148 & 149 & 149 \\ \hline
3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
  & Popular Youtube   & 3   & 20  & 18  \\ \hline
  & Twitch.tv         & 149 & 148 & 0   \\ \hline
  & Soundcloud        & 148 & 148 & 148 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 190.9   \\ \hline
  & Popular Youtube   & 8048.6  \\ \hline
  & Twitch.tv         & 10526.7 \\ \hline
  & Soundcloud        & 1341.4  \\ \hline
2 & Unpopular Youtube & 9513.0  \\ \hline
  & Popular Youtube   & 8335.4  \\ \hline
  & Twitch.tv         & 11397.1 \\ \hline
  & Soundcloud        & -       \\ \hline
3 & Unpopular Youtube & 9840.6  \\ \hline
  & Popular Youtube   & 7260.2  \\ \hline
  & Twitch.tv         & 11274.2 \\ \hline  
  & Soundcloud        & -       \\ \hline
\end{tabular}

\section{Future Work}\label{sec:futurework}
\begin{itemize}
	\item Streaming (e.g incorporate youtube life or twitch non-vods)
	\item Video content vs video adverts
	\item Test from multiple locations
\end{itemize}
